Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-28 paper/AlignedIsotropicGW.tex
Better calculations in the O.M. section.

If the true distribution is isotropic and follows this simple model,
and our measurement uncertainties on $\chieff$ are $\simeq 0.2$, then
each subsequent measurement contributes on average a factor of
$\sim 2.5$ to the overall odds.  (There is a 1/3 chance each of the
critical value of $\chieff = 0$ lying at $-1\sigma$, $0$, and
$+1\sigma$ with respect to the centre of the posterior.)  After ten
additional events, then, the odds ratio becomes
$5 \times 2.5^{10} \simeq 5 \times 10^{5}$, or $4.3 \sigma$,
consistent with the results of the more detailed calculation described
above.

>>>>

If the true distribution is isotropic and follows this simple model,
and our measurement uncertainties on $\chieff$ are $\simeq 0.1$, then
each subsequent measurement contributes on average a factor of
$\sim 3$ to the overall odds.  After ten additional events, then, the
odds ratio becomes $5 \times 3^{10} \simeq 3 \times 10^{5}$, or
$4.6 \sigma$, consistent with the results of the more detailed
calculation described above.  If the true distribution of spins
becomesf half as wide ($\chieff \in [-0.125, 0.125]$ for isotropic and
$\chieff \in [0, 0.25]$ for aligned spins), with the same
uncertainties, then the existing odds ratio becomes $1.08$, and each
subsequent event drawn from the isotropic distribution contributes on
average a factor of $1.6$.  In this case, after 10 additional events,
the odds ratio becomes $150$, or $2.7\sigma$.  With small spin
magnitudes, our angular resolving power vanishes.
